A meta analysis of tournaments and an evaluation of performance in the Iterated Prisoner's Dilemma.

### 2020-01-16 paper/main.tex
address comments on pr

The result summary, Table~\ref{table:output_result}, has \(N\) rows
because each row contains information for each strategy that participated in the
tournament. The information includes the strategy's rank, median score, the rate
with which the strategy cooperated $(C_r)$, its match win count and the
probability that the strategy cooperated in the opening move. Moreover, the
probabilities of a strategy being in any of the four states ($CC, CD, DC, DD$),
and the rate of which the strategy cooperated after each state. A feature that
has been manually included is the \textbf{normalised rank}. The rank of a given
strategy, denoted as \(R\), can vary between 0 and \(N-1\). Thus, the normalised rank,
denoted as $r$, is calculated as a strategy's rank divided by the tournament's
size $N$ minus 1. In the next section the performance of these strategies is evaluated
based on their normalised rank.

@@

This manuscript has explored the performance of \numberofstrategies strategies of the Iterated
Prisoner's Dilemma in a large number of computer tournaments. The results of
the analysis demonstrated that, although for specific tournament types such as
standard and probabilistic ending tournaments, dominant strategies exist
there is not a single dominant type of strategies if the environments
vary. Moreover, a strategy with a theory of mind should aim to adapt its behaviour
based on the mean and median cooperators.

The \numberofstrategies strategies used in this manuscript have been mainly from
the literature, and they have been accessible due to an open source software
called Axelrod-Python library. The software was used to generate a total of
\numberofalltournaments computer tournaments results with different number of
strategies and different participants each time. The data collection was
described in Section~\ref{section:data_collection}. In
Section~\ref{section:top_performances}, the tournaments results were used to
present the top performances. The data set contained results from four different
settings, and these were also studied individually. In standard tournaments
complex strategies trained using reinforcement learning ranked in the top spots.
Some of these strategies ranked again in the top spots in probabilistic
ending tournaments when a \(p_e\) of less 0.1 was considered. In probabilistic
ending tournaments \(p_e\) was designed to vary between 0 and 1. It was demonstrated
that for values larger than 0.1, as stated in the Folk Theorem, defecting strategies
were winning the tournaments because there was a high likelihood of the game
ending in the next turn. In tournaments with noise the median ranks of the top
15 strategies had the highest values and the \(r\) distributions were bimodal.
The top rank strategies were performing both well and bad, and this indicates
that in noisy tournaments there are not strategies that can guarantee winning.
Overall, the top ranked strategies differed from one tournament type to
another and the mechanism behind the winning strategies were all different.
Even strategies designed to do good in one setting did better in others.
On the whole ... (the ipd interactions are unique and there is no winning
strategy) %TODO help from Vince

Section~\ref{section:evaluation_of_performance}, covered an analysis of
performance based on several features associated with a strategy and with the
environments it was competing. The results of this analysis showed that a
strategy's characteristics such as whether or not it's stochastic, and the information it
used regarding the game had no effect on the strategy's success. The most
important features have been those that compared the strategy's behaviour to it's
environment. The cooperating ratio of the strategy compared to the mean and
median cooperator was highlighted as the most important feature in the analysis.
More specifically, if a strategy were to enter a tournament with a theory of
mind of its environment it would choose to be the median cooperator in standard
tournaments, to cooperate 10\% of the times the median cooperator did in probabilistic ending tournaments and 
60\% in noisy and noisy probabilistic
tournaments. Lastly, if a strategy was aware of the opponents but not of the
setting on the tournament, a strategy would be more likely to be successful if
it were to identify the median cooperator and cooperated 67\% of the times that
they did.

>>>>

The result summary, Table~\ref{table:output_result}, has \(N\) rows
because each row contains information for each strategy that participated in the
tournament. The information includes the strategy's rank, median score, the rate
with which the strategy cooperated $(C_r)$, its match win count and the
probability that the strategy cooperated in the opening move. Moreover, the
probabilities of a strategy being in any of the four states ($CC, CD, DC, DD$),
and the rate of which the strategy cooperated after each state. A feature that
has been manually included is the \textbf{normalised rank}. The rank of a given
strategy, denoted as \(R\), can vary between 0 and \(N-1\). Thus, the normalised rank,
denoted as $r$, is calculated as a strategy's rank divided by the tournament's
size \(N - 1\). In the next section the performance of these strategies is evaluated
based on their normalised rank.

@@

This manuscript has explored the performance of \numberofstrategies strategies of the Iterated
Prisoner's Dilemma in a large number of computer tournaments. The results of
the analysis demonstrated that, although for specific tournament types such as
standard and probabilistic ending tournaments, dominant strategies exist
there is not a single dominant type of strategies if the environments
vary. Moreover, a strategy with a theory of mind should aim to adapt its behaviour
based on the mean and median cooperators and should in general not be too
cooperative.

The \numberofstrategies strategies used in this manuscript have been mainly from
the literature, and they have been accessible due to an open source software
called the Axelrod-Python library. The software was used to generate a total of
\numberofalltournaments computer tournaments results with different number of
strategies and different participants each time. The data collection was
described in Section~\ref{section:data_collection}. In
Section~\ref{section:top_performances}, the tournaments results were used to
present the top performances. The data set contained results from four different
settings, and these were also studied individually. In standard tournaments
complex strategies trained using reinforcement learning ranked in the top spots.
Some of these strategies ranked again in the top spots in probabilistic
ending tournaments when a \(p_e\) of less 0.1 was considered. In probabilistic
ending tournaments \(p_e\) was designed to vary between 0 and 1. It was demonstrated
that for values larger than 0.1, as stated in the Folk Theorem, defecting strategies
were winning the tournaments because there was a high likelihood of the game
ending in the next turn. In tournaments with noise the median ranks of the top
15 strategies had the highest values and the \(r\) distributions were bimodal.
The top rank strategies were performing both well and bad, and this indicates
that in noisy tournaments there are not strategies that can guarantee winning.
Overall, the top ranked strategies differed from one tournament type to
another and the mechanism behind the winning strategies were all different.
Even strategies designed to do good in one setting did better in others.
On the whole ... (the ipd interactions are unique and there is no winning
strategy) %TODO help from Vince

Section~\ref{section:evaluation_of_performance}, covered an analysis of
performance based on several features associated with a strategy and with the
environments it was competing. The results of this analysis showed that a
strategy's characteristics such as whether or not it's stochastic, and the information it
used regarding the game had no effect on the strategy's success. The most
important features have been those that compared the strategy's behaviour to it's
environment. The cooperating ratio of the strategy compared to the mean and
median cooperator was highlighted as the most important feature in the analysis.
More specifically, if a strategy were to enter a tournament with a theory of
mind of its environment it would choose to be the median cooperator in standard
tournaments, to cooperate 10\% of the time the median cooperator did in probabilistic ending tournaments and 
60\% in noisy and noisy probabilistic
tournaments. Lastly, if a strategy was aware of the opponents but not of the
setting of the tournament, a strategy would be more likely to be successful if
it were to identify the median cooperator and cooperated 67\% of the times that
they did.
